### 2020-04-20 tbf.tex
minor correction in tbf section

\begin{figure}[bt]
  \begin{center}
    \includegraphics[width=\columnwidth]{figs/MTBF_quaterly_sys.pdf}
  \end{center}
  \caption{Variation of system-wide MTBF over the lifetime of the machine (time is segmented into quarters, 
i.e., January through April is Q1 and so on).}
  \label{fig:MTBF_sys}
\end{figure}

@@

That said, a single MTBF number does not give an accurate picture of this machine.
With many GPU relocations and replacements across the machine over its lifetime, it is 
best to consider the variation of MTBF across fixed periods. Herein, we calculate 
the mean of time-between-failures across four months. Figure~\ref{fig:MTBF_sys}
clearly shows the considerable change in system-wide MTBF from one period to another. 
The observation of the MTBF trend shows the different phases which the machine went through. 
For example, when considering failure due to both DBE and OTB events more than 4X drop in MTBF is 
noted from 2015-Q3 to 2015-Q4 (note, MTBF of earlier quarters was significantly higher and is not 
included in the figure to better visualize various change points). This period marked the start of 
a rapid decline in system-wide MTBF until 2016-Q4. The rapid rise of the number of failures before this 
quarter can be seen in Figure~\ref{fig:NumFails_sys}. When GPU replacements start to take place in late 
2016, it triggers an increase in MTBF. However, this change only lasts until 2018-Q1, when we see another 
downward trend of system MTBF. Incidentally, 2018-Q1 also marks the completion of all GPU replacements. 
So the upward trend noted in the period from 2016-Q4 to 2018-Q1 might be attributed to a portion of the machine 
being unavailable while the reworks were taking place. A single replacement cycle lasted multiple weeks. 
\fix{need to verify how long the replacement took}
There is no definite way to incorporate this unavailability of the machine into MTBF analysis, so it has to
be said that overall there has been an increase in MTBF of the machine due to the replacements. 
For example, before 2017-Q1 MTBF as low as 2.7 hours is noted, whereas the lowest MTBF is 5.9 hours after this 
period. With such huge variations in system MTBF, it is difficult to reliably run applications even while using 
failure recovery approaches such as checkpoint restart, as discussed later on in Section~\ref{section:discussion}.

>>>>

\begin{figure}[bt]
  \begin{center}
    \includegraphics[width=\columnwidth]{figs/MTBF_quaterly_sys.pdf}
  \end{center}
  \caption{Variation of system-wide MTBF over the lifetime of the machine (time is segmented into quarters, 
i.e., January through March is Q1 and so on).}
  \label{fig:MTBF_sys}
\end{figure}

@@

That said, a single MTBF number does not give an accurate picture of this machine.
With many GPU relocations and replacements across the machine over its lifetime, it is 
best to consider the variation of MTBF across fixed periods. Herein, we calculate 
the mean of time-between-failures across three months. Figure~\ref{fig:MTBF_sys}
clearly shows the considerable change in system-wide MTBF from one period to another. 
The observation of the MTBF trend shows the different phases which the machine went through. 
For example, when considering failure due to both DBE and OTB events more than 4X drop in MTBF is 
noted from 2015-Q3 to 2015-Q4 (note, MTBF of earlier quarters was significantly higher and is not 
included in the figure to better visualize various change points). This period marked the start of 
a rapid decline in system-wide MTBF until 2016-Q4. The rapid rise of the number of failures before this 
quarter can be seen in Figure~\ref{fig:NumFails_sys}. When GPU replacements start to take place in late 
2016, it triggers an increase in MTBF. However, this change only lasts until 2018-Q1, when we see another 
downward trend of system MTBF. Incidentally, 2018-Q1 also marks the completion of all GPU replacements. 
So the upward trend noted in the period from 2016-Q4 to 2018-Q1 might be attributed to a portion of the machine 
being unavailable while the reworks were taking place. A single replacement cycle lasted multiple weeks. 
\fix{need to verify how long the replacement took}
There is no definite way to incorporate this unavailability of the machine into MTBF analysis, so it has to
be said that overall there has been an increase in MTBF of the machine due to the replacements. 
For example, before 2017-Q1 MTBF as low as 2.7 hours is noted, whereas the lowest MTBF is 5.9 hours after this 
period. With such huge variations in system MTBF, it is difficult to reliably run applications even while using 
failure recovery approaches such as checkpoint restart, as discussed later on in Section~\ref{section:discussion}.
